A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2021-11-22 analysis/paper/paper.Rmd
Assembled preliminary results plot

Previous evaluations of the correspondence between dates informed by radiocarbon dates and shoreline dating have typically involved a visual inspection of radiocarbon probability distributions plotted against local shoreline displacement curves based on the site elevation [@breivik2018; @solheim2020; @åstveit2018\]. This approach has a couple of limitations. Firstly, only a couple of studies have taken the variable uplift-rates into account when performing this comparison . Secondly, the question of interest in this case is effectively one of synchroneity between events, as opposed to difference \[@parnell2008]. This framing consequently flips the direction of the common null-hypothesis of no significant difference too one of equivalence. While two overlapping confidence intervals means that one cannot conclude that they are different, this does not necessarily mean that they are the same. One implication of this method is consequently that the wider the uncertainty range for either radiocarbon- or shoreline date, the higher the liklihood that the confidence intervals overlap, and the higher the likelihood that we conclude in favour of our hypothesis. The final limitation of this method is that it only takes the vertical distance between site and shoreline into account. While this is the parameter of interest for shoreline dating, the practical implications of a vertical difference in elevation will be highly dependent on the local topography.

>>>>

Previous evaluations of the correspondence between dates informed by radiocarbon dates and shoreline dating have typically involved a visual inspection of radiocarbon probability distributions plotted against local shoreline displacement curves based on the site elevation [e.g. @breivik2018; @solheim2020; @åstveit2018\]. This approach has a couple of limitations. First of all, only a couple of studies have taken the variable uplift-rates into account when performing this comparison. Secondly, following this method, the wider the uncertainty range associated with either radiocarbon- or shoreline date, the higher the probability that the confidence intervals overlap, and the higher the probability that we conclude in favour of our hypothesis. While two overlapping confidence intervals means that one cannot conclude that the dates are different, this does not necessarily mean that they are the same. The question thus necessitates a flip from a null-hypothesis of no signficant difference to one of equivalence, as the question of interest in this case is effectively one of synchroneity \[cf. @parnell2008]. A final limitation of this method is that it only takes into account the vertical distance between site and shoreline. While this is the parameter of interest for shoreline dating, the practical implications of a vertical difference in elevation will be highly dependent on local topography and bathymetry.
